???A quantitative framework for investigating the reliability of network construction

### 2017-09-17 manuscript/CI_interactions.tex
changes to the ms outline

@@

\section{Why some interactions do not occur ?}

@@

>>>>

\section*{Different uncertainties in computing a network}

THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD. DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.

\section*{Why some interactions do not occur ?}

@@

\section*{Estimating detection and process uncertainty}

@@

\section*{Scaling up uncertainty from pairwise interactions to networks}
